\documentclass [a4paper, twoside] {book}

\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage[italian]{babel}
\usepackage{array}
\usepackage{color}
\usepackage{colortbl}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{siunitx}
\usepackage{hyperref}
\usepackage{microtype}
\usepackage{listings}
\usepackage{adjustbox}
\usepackage{verbatim}
\usepackage{float}
\usepackage{mathrsfs}
\usepackage{titling}
\usepackage{etoolbox}
\usepackage[a4paper,top= 3cm,bottom= 2cm,left= 2cm,right= 2cm]{geometry}
\newcommand{\subtitle}[1]{%
  \posttitle{%
    \par\end{center}
    \begin{center}\large#1\end{center}
    \vskip0.5em}%
}

\title{Appunti di Istituzioni di Fisica Applicata}
\subtitle{Dalle lezioni del prof. Riccardo Faccini}
\author{Manuel Loparco}

\begin{document}
\maketitle

\tableofcontents
\mainmatter

\include{Introduzione}

\include{Unita_naturali}

\include{Interazioni_radiazione_materia}

\include{Decadimenti_nucleari}

\include{Reazioni_nucleari}

\include{Dosimetria}

\include{Fisica_neutroni}


\begin{thebibliography}{35}


\bibitem{ENMP}
R.Powsner, E.Powsner 
\textit{Essential Nuclear Medicine Physics}
 (2nd edition), Wiley (2006)

\bibitem{NMP}
D.L. Bailey et al
\textit{Nuclear Medicine Physics}.
IAEA\\
 \textit{https://www-pub.iaea.org/MTCD/Publications/PDF/Pub1617web-91160047.pdf}

\bibitem{CLA}
\textit{Cyclotrons, LINACs and their applications}
CAS 1994\\ \textit{https://www.dropbox.com/s/zpr104qgfhon852/CERN-96-02.pdf?dl=0}

\bibitem{PET1}
H. Jadvar, J.A. Partker
\textit{Clinical PET and PET-CT}
Sprigler 2006

\bibitem{PET2}
D.Bailey, D.W.Townsend, P.E.Valk, M.N.Maisey
\textit{Positron Emission Tomography}
Springer (2005)

\bibitem{CT}
F. Natterer
\textit{The mathematics of Computerized Tomography}
SIAM 2001

\bibitem{Rossi}
Adrontherapy course by Sandro Rossi to INFN Rome (2013)
\\ \textit{https://agenda.infn.it/event/6405/attachments/45601/}

\bibitem{Braccini}
Adrontherapy course by Saverio Braccini to INFN Rome (2012)
\\ \textit{https://agenda.infn.it/event/2255/attachments/27899/}

\bibitem{ADRO}
Impact of nuclear reactions on Hadron Therapy (2008)
\\ \textit{http://www.lpc-caen.in2p3.fr/root/.EJC2011-CUSSOL/EJC2011\_CUSSOL.pdf}

\bibitem{Dosimetria per protonterapia}
Knopf and Lomax,
\textit{Dosimetry for protontherapy}
\\ \textit{http://iopscience.iop.org/article/10.1088/0031-9155/58/15/R131/meta}

\bibitem{Dosimetria per adronterapia}
Faccini and Patera
\textit{Dosimetry for hadrontherapy}
\\ \textit{https://elearning.uniroma1.it/pluginfile.php/138728/mod\_page/content/14/Review$\%$20Dosimetria$\%$20per$\%$20HT$\%$20$\%$28FP$\%$29.pdf}

\bibitem{Boron}
IAEA Report
\textit{Boron Neutron Capture Therapy}
\\ \textit{https://elearning.uniroma1.it/pluginfile.php/138728/mod\_page/content/14/te\_1223\_prn.pdf}

\bibitem{Acceleratori per adronterapia}
\textit{Review of Accelerators for Hadron Therapy}
\\ \textit{https://elearning.uniroma1.it/pluginfile.php/138728/mod\_page/content/14/review\_accelerators\_HT.pdf}

\bibitem{LINAC}
\textit{LINAC for protontherapy}
\\ \textit{https://elearning.uniroma1.it/pluginfile.php/138728/mod\_page/content/14/TULIP\_LINAC\_PT.pdf}

\bibitem{Radiosurgery}
G. Mariani, A. E. Giuliano, H.W. Strauss,
\textit{Radioguided surgery a comprehensive team approach}
Springer 2006

\bibitem{Intraoperative probes}
E. Hoffman et al,
\textit{Intraoperative probes and imaging probes}
Eur. J. Nucl. Med. 26, 913–935 (1999)

\bibitem{Brachioterapia}
Y. Watanabe
\textit{Brachytherapy Physics}
\\ \textit{https://www.slideshare.net/hikikomorijcv18/brachytherapy-30581870}

\bibitem{Cultural}
EPS review
\textit{Nuclear Physics for Cultural Heritage}
\\ \textit{https://www.edp-open.org/images/stories/books/fulldl/Nuclear-physics-for-cultural-heritage.pdf}

\bibitem{Longo}
E. Longo e C. Dionisi
\textit{Dispense del corso di Laboratorio di Fisica Nucleare e Subnucleare, Chap. 4}
\\ \textit{http://www.roma1.infn.it/people/longo/fnsn/capitolo4.pdf}

\bibitem{Beringer}
J. Beringer et al. (Particle Data Group)
\textit{Passage of particles through matter, Chap. 31}
Phys. Rev. D86, 010001 (2012)
\\ \textit{http://pdg.lbl.gov/2013/reviews/rpp2013-rev-passage-particles-matter.pdf}

\bibitem{Amaldi}
U. Amaldi
\textit{Radiation Physics: Photons and Charged Hadrons}
2001 \\ \textit{https://physique.cuso.ch/fileadmin/physique/document/Amaldi-Rad.-Trento-2001.pdf}

\bibitem{Corvisiero}
P. Corvisiero
\textit{Interazioni Neutroni Materia, Chap. 14}
\\ \textit{https://www.ge.infn.it/~corvi/doc/didattica/radioattivita/lezioni/}

\bibitem{Assay}
Passive Nondestructive Assay Manual
\textit{Neutrons Interactions with Matter}
\\ \textit{https://www.lanl.gov/orgs/n/n1/panda/}

\bibitem{Beringer2}
J. Beringer et al. (Particle Data Group)
\textit{Particle Detectors at Accelerators}
Phys. Rev. D86, 010001 (2012), Chap. 32
\\ \textit{http://pdg.lbl.gov/2013/reviews/rpp2013-rev-particle-detectors-accel.pdf}

\bibitem{Knoll}
G.F. Knoll
\textit{Radiation Detection and Measurement}

\bibitem{Corvisiero2}
P. Corvisiero
\textit{Appunti di Radiativita', Chap. 18}
\\ \textit{https://www.ge.infn.it/~corvi/doc/didattica/radioattivita/lezioni/}

\bibitem{Beringer3}
J. Beringer et al. (Particle Data Group)
\textit{Radiactivity and radiation protection, Chap. 34}
Phys. Rev. D86, 010001 (2012)
\\ \textit{http://pdg.lbl.gov/2013/reviews/rpp2013-rev-radioactivity.pdf}

\bibitem{Films}
P. Fattibene, C. De Angelis,
\textit{Film Dosimetria}
\\ \textit{https://elearning.uniroma1.it/pluginfile.php/137557/mod\_page/content/17/DosimetriFilm.pdf}

\bibitem{TLD}
\textit{Dosimetria a Termoluminescenza}
\\ \textit{https://elearning.uniroma1.it/pluginfile.php/137557/mod\_page/content/17/DosimetriTLD.pdf}

\bibitem{Laitano}
R.F. Laitano,
\textit{Fondamenti di Dosimetria delle radiazioni ionizzanti}
\\ \textit{http://www.enea.it/it/seguici/pubblicazioni/pdf-volumi/FondamentidosimetriaradiazioniionizzantiIV.pdf}

\bibitem{Corvisiero3}
P. Corvisiero,
\textit{Le leggi del decadimento radiativo, Chap. 1,2}
\\ \textit{https://www.ge.infn.it/~corvi/doc/didattica/radioattivita/lezioni/}

\bibitem{Nutshell}
A. Bertulani,
\textit{Nuclear Physics in a Nutshell, Chap. 6}

\bibitem{Ferrario}
M. Ferrario,
\textit{Accelerator Physics: Basic Principles on Beam Focusing and Transport}
\\ \textit{https://elearning.uniroma1.it/pluginfile.php/137557/mod\_page/content/17/8\_SPARC-BD-12-01.pdf}

\bibitem{Wilson}
E. Wilson,
\textit{An Introduction to Particle Acceleration}
2001

\bibitem{Rosemblatt}
J. Rosemblatt,
\textit{Particle Acceleration}
1968




\end{thebibliography}


\end{document}













